\documentclass[boxes]{gsypset}

\mailbox{}
\class{Math 65}
\assignment{HW 3}
\duedate{May 19}

\begin{document}

\problemlist{3.1.\{3, 10, 17\}, 3.2.\{1, 4, 13\}, 3.3.\{9, 18, 20\}}

\begin{problem}[3.1.3]
	Sketch the image of the following path, using
	arrows to indicate the direction in which the parameter increases:
	\[
		\begin{cases}
			x=t\cos t\\
			y=t\sin t
		\end{cases},
		\quad-6\pi\leq t\leq6\pi
	\]
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.1.10]
	Calculate the velocity, speed, and acceleration of the given path.
	\[
		\mathbf{x}(t)=(e^t,e^{2t},2e^t)
	\]
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.1.17]
	Find an equation for the line tangent to the
	given path at the indicated value for the parameter.
	\[
		\mathbf{x}(t)=(t^2,t^3,t^5),t=2
	\]
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.2.1]
	Calculate the length of the given path.
	\[
		\mathbf{x}(t)=(2t+1,7-3t),-1\leq t\leq2
	\]
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.2.4]
	Calculate the length of the given path.
	\[
		\mathbf{x}(t)=7\mathbf{i}+t\mathbf{j}+t^2\mathbf{k},1\leq t\leq3
	\]
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.2.13]
	This problem concerns the path 
	\[
		\mathbf{x} = |t-1|\mathbf{i} + |t|\mathbf{j}, \quad -2 \leq t \leq 2
	\]
	\begin{enumerate}
		\item Sketch this path.
		\item The path fails to be of class $C^1$ but is piecewise $C^1$.
			Explain.
		\item Calculate the length of the path.
	\end{enumerate}
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.3.9]
	Sketch the given vector field on $\mathbb{R}^3$.
	\textit{Note:} describe in addition to sketch.
	\[
		\mathbf{F}=(0,z,-y)
	\]
\end{problem}
\begin{solution}
	
\end{solution}

\begin{problem}[3.3.18]
	Verify that the path given is a flow line of the indicated vector field. 
	Justify the result geometrically with an appropriate sketch.
	\[
		\mathbf{x}(t)=(\sin t,\cos t,2t),\mathbf{F}=(y,-x,2)
	\]
\end{problem}
\begin{solution}
	
\end{solution}


\begin{problem}[3.3.20]
	Calculate the flow line $\mathbf{x}(t)$ of the given vector field $\mathbf{F}$
	that passes through the indicated point at the specified value of $t$.
	\[
		\mathbf{F}(x,y)=-x\mathbf{i}+y\mathbf{j};\quad\mathbf{x}(0)=(2,1)
	\]
\end{problem}
\begin{solution}
	
\end{solution}
\end{document}
